\Title

### 2021-01-25 manuscript/manuscript.tex
Describe the source layouts so we don't need the table

The combination of the three source layouts with the three strategies to define
the depth of the sources define seven different source distributions (see
Table~\ref{tab:source-distributions}).
The \emph{grid sources} is only compatible with the \emph{constant depth}
scheme if no further information is provided.

\begin{table*}
    \centering
    \caption{
        Source distributions as combinations of source layouts and depth
        strategies.
    }
    \label{tab:source-distributions}
    \begin{tabular}{lccc}
        & Source below data & Block averaged sources & Grid sources \\ \hline
        Constant depth & $\checkmark$ & $\checkmark$ & $\checkmark$ \\
        Relative depth & $\checkmark$ & $\checkmark$ & $\times$     \\
        Variable depth & $\checkmark$ & $\checkmark$ & $\times$     \\
    \end{tabular}
\end{table*}

>>>>

We investigated the effect of different strategies for distributing the
equivalent sources horizontally and vertically on interpolation accuracy.
To do this, we used the damped least-squares solution described in
Section~\ref{sec:eql_inversion} (without gradient boosting) to interpolate the
synthetic datasets (Fig.~\ref{fig:synthetic-layouts}) and compared the results
against the target grid (Fig.~\ref{fig:synthetic-target}).
This process was repeated for each combination of horizontal layout
(sources-below-data and block-averaged-sources) and depth type (constant,
relative, and variable) and for regular-grid sources with a constant depth,
totalling 7 different combinations.
